---
title: "Pohatu Penguins Monitoring Data Analysis"
author: "Rachel Hickcox"
date: "2022"
email: "rphickcox@gmail.com"
editor_options: 
  chunk_output_type: console
---

### Load packages
```{r pkg, eval=TRUE, message=FALSE, warning=FALSE, cache=FALSE}
pkgs <- c("knitr", "kableExtra", "broom", 
          "readxl", "flextable", "terra", "googlesheets4", "googledrive", 
          "lubridate", "tidyverse", "openxlsx")
new.packages <- pkgs[!(pkgs %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
invisible(lapply(pkgs, library, character.only = TRUE))
rm(list = c("pkgs", "new.packages"))
options(scipen = 999)
```

### Connecting to Google Drive
```{r googledrive}
drive_auth(email = "pohatumonitoring@gmail.com")

drive_download(file = "https://docs.google.com/spreadsheets/d/1mEcD3r8sAauUH_rE5dDMkvpPlYNVqrEXawA0CYAg34E", 
               overwrite = TRUE, 
               path = "./../ALL_DATA/Data/Monitoring.xlsx")
monitor <- read_excel("./../ALL_DATA/Data/Monitoring.xlsx")

drive_download(file = "https://docs.google.com/spreadsheets/d/1qh6zAXgVokfdx4WjjSls8qh4tAfEOL-bO3xg3CvRY44", 
               overwrite = TRUE,
               path = "./../ALL_DATA/Data/Nest ID.xlsx")
nestid <- read_excel("./../ALL_DATA/Data/Nest ID.xlsx")

nestid2 <- nestid %>% 
  separate(col = Location, into = c("Lat", "Lon"), sep = ",", remove = FALSE) %>% 
  mutate(Lat = ifelse(str_detect(`Nest ID`, "^DUD"), NA, Lat), 
         Lon = ifelse(str_detect(`Nest ID`, "^DUD"), NA, Lon)) %>% 
  arrange(`Nest ID`)
write.csv(nestid2, "./../ALL_DATA/Data/Nest ID.csv")

drive_download(file = "https://docs.google.com/spreadsheets/d/16c4c5nXbz_PFf7iyN2DG7fExsi4P5uP-NSYAbCDX1rc", 
               overwrite = TRUE, 
               path = "./../ALL_DATA/Bird ID.xlsx")
birdid <- read_excel("./../ALL_DATA/Bird ID.xlsx")
```

### Setup
```{r setup}
# Dates
tdt <- floor_date(today(), "weeks", week_start = 1) # lubridate start of week
tdt_d <- format(tdt, "%d-%m-%Y") # character today's start of week date 
tdt_s <- as.numeric(str_replace_all(as.character(tdt), pattern = "-", "")) # string
yr <- ifelse(month(today()) > 8, year(today()), year(today())-1) # yr
start <- floor_date(as.Date(paste0("01-08-", yr), "%d-%m-%Y"), "weeks", week_start = 1) # start date
end <- as.Date(paste0("01-09-", yr + 1), "%d-%m-%Y")
non_br <- as.Date(paste0("01-04-", yr + 1), "%d-%m-%Y")
dates_df <- seq(start, today(), 7)
```

### CHOOSING NEST YEAR
```{r ny}
yr <- ifelse(month(today()) > 8, year(today()), year(today())-1) # yr
#yr <- 2022
```


### Nests summary
```{r nests}
# Nest coords 
nestid_coord <- nestid %>%
  tidyr::separate(Location, into = c("Lat", "Long"), ",") %>%
  dplyr::select(`Nest ID`, Lat, Long) %>%
  mutate(Lat = as.numeric(Lat), Long = as.numeric(Long))

nests <- monitor %>%
  distinct(across(DateTime:`Chick 4 weight`), .keep_all = TRUE) %>%
  mutate(NestYear = ifelse(month(DateTime) > 7, year(DateTime), year(DateTime)-1),
         FullID = paste0(NestYear, `Nest ID`), 
         Eggs = ifelse(is.na(Eggs), 0, as.numeric(Eggs)), 
         Chicks = ifelse(is.na(Chicks), 0, as.numeric(Chicks))) %>%  #not visible to NA, error ok
  group_by(FullID) %>%
  arrange(`Nest ID`, DateTime) %>%
  mutate(n = row_number()) %>%
  mutate(n1 = ifelse(`Nest activity` == "Eggs/Chicks present", n, NA)) %>%
  filter(NestYear != 2021) %>%
  #error for nests never breeding, n1 is inf, error ok
  filter(n >= min(n1, na.rm = TRUE)-1, n <= max(n1, na.rm = TRUE)+1) %>% 
  mutate(Date_last = lag(DateTime), .before = DateTime) %>% 
  # filter(`Nest activity` == "Eggs/Chicks present" | 
  #          `Nest activity` == "FAILED" | 
  #          `Nest activity` == "Empty") %>%
  mutate(`Nest activity` = ifelse(Interaction == "Uplifted", 
                                  "Uplifted",`Nest activity`)) %>%
  # Flag where a new nest starts
  mutate(NewNestFlag = case_when(
    `Nest activity` %in% c("Eggs/Chicks present", "Uplifted", "Marking") & (lag(`Nest activity`) %in% c(NA, "Loafing adult(s)", "FAILED", "Moulting")) ~ 1,
    TRUE ~ 0),
    # Increment only at the last occurrence of NA/Not breeding before a new nest starts
    Nest_number = cumsum(NewNestFlag)
  ) %>%
  #ungroup() %>%
  mutate(Nest_number = ifelse(Nest_number == 0, NA, Nest_number), 
         NestID_count = n_distinct(Nest_number, na.rm = TRUE)) %>%  # Count distinct Nest_numbers per FullID
  mutate(FullID = ifelse(NestID_count > 1 & !is.na(NestID_count), paste(FullID, Nest_number, sep = "_"), FullID)) %>%
  select(-c(NewNestFlag, NestID_count, Nest_number)) # Remove temporary column after use


nests <- nests %>%
  mutate(.after = 2,
         DateTime = as.Date(DateTime),
         Week = ifelse(year(DateTime) > yr, week(DateTime)+52, week(DateTime)),
         Date_last = difftime(as.Date(DateTime), as.Date(Date_last), units = "days"), 
         Est_LayDate = as.Date(first(DateTime[`Nest activity` == "Eggs/Chicks present"]), na.rm = TRUE)) %>%
  mutate(.after = Est_LayDate, Est_HatchDate = Est_LayDate + 35) %>% 
  dplyr::select(NestYear, FullID, `Nest ID`, Date_last:Est_HatchDate, `Nest activity`:`Adult 1`, 
                `Adult 2`, Eggs:`Chick 1 weight`, `Chick 2 ID`:`Chick 2 weight`,
                Notes, n, n1) %>%
  mutate(Status = ifelse(Eggs > 0, "Eggs", NA), 
         Status = ifelse(Chicks > 0, "Chicks", Status), 
         .before = 2) %>% 
  left_join(nestid_coord, by = "Nest ID") %>% 
  mutate(n2 = lag(Chicks)) %>% 
  group_by(FullID) %>% 
  mutate(`Nest activity` = ifelse(lag(`Nest activity`) == "FAILED" & 
                                    `Nest activity` == "FAILED", NA, `Nest activity`),
         Status = ifelse(is.na(`Nest activity`), NA, Status),
         Status = ifelse(is.na(n1) & n2 > 0, "Fledged", Status),
         Status = ifelse(`Nest activity` == "FAILED", "Failed", Status), 
         Status = ifelse(`Nest activity` == "Uplifted", `Nest activity`, Status),
         #if failed followed by empty, removing all empty rows (i.e., did not fledge)
         nn = ifelse(lag(`Nest activity`) == "FAILED" & 
                       `Nest activity` == "Empty", "R", NA),
         #if uplifted followed by empty, removing all empty rows (i.e., did not fledge)
         nn = ifelse(lag(`Nest activity`) == "Uplifted" & 
                       `Nest activity` == "Empty", "R", nn),
         #if row fledged but was previously uplifted, changing status to the previous status (i.e., did not fledge before uplift)
         Status = ifelse(Status == "Fledged" & 
                           `Nest activity` %in% "Uplifted", lag(Status), Status),
         nn = unlist(nn), 
         NHatched = ifelse(max(Chicks, na.rm = T) > 2, 2, max(Chicks, na.rm = T)), 
         NLaid = ifelse(NHatched == 2, 2, max(Eggs, na.rm = T))) %>% 
  filter(!is.na(Status), is.na(nn)) %>% 
  filter(!is.na(Date_last)) %>% 
  dplyr::select(-c(n, n1, n2, nn))
```

### Nests failed
```{r failed}
# Failed nests 
failed_nests <- nests %>%
  filter(Status == "Failed") %>% # | Status == "Uplifted") %>%
  #dplyr::select(NestYear, `Nest ID`, `Nest activity`, DateTime) %>% 
  dplyr::select(-c(Date_last, Week, `Nest activity`)) %>% 
  arrange(NestYear, `Nest ID`, DateTime) %>%
  group_by(FullID) %>% 
  filter(DateTime == min(DateTime))
#clipr::write_clip(failed_nests)
```

### Nests with eggs
```{r eggs}
eggs <- nests %>% 
  filter(Eggs != 0 & Status != "Chicks") %>% 
  dplyr::select(NestYear, DateTime, FullID, `Nest ID`, Status, Est_LayDate:Est_HatchDate, 
                Eggs, Chicks, NLaid, NHatched, Notes) %>% 
  distinct(across(NestYear:Chicks), .keep_all = T) %>%
  group_by(FullID) %>% 
  arrange(NestYear, `Nest ID`, DateTime) %>% 
  mutate(HatchDate = NA, .after = Est_HatchDate, 
         Est_TranspondDate5 = Est_HatchDate + 35,
         Est_TranspondDate6 = Est_HatchDate + 42,
         Est_FledgeDate = Est_HatchDate + 56, 
         Eggs_1 = lag(as.numeric(Eggs)),
         Eggs_2 = as.numeric(Eggs)) %>% 
  mutate(diffeggs = as.numeric(Eggs) - lag(as.numeric(Eggs)), .after = Eggs_2, 
         Comments = "", 
         Comments = ifelse(Status != "Failed" & diffeggs < 0, 
                           paste0(diffeggs, " eggs on ", DateTime, "."), NA), 
         Comments = replace_na(Comments, ""),
         Comments = ifelse(Status == "Failed" , 
                           paste0(Comments, "Failed (eggs) on ", DateTime, "."),
                           Comments), 
         Comments = paste(Comments, collapse = " "),
         Status2 = ifelse(any(Status =="Failed"), "Failed", Status),
         nn = row_number(), 
         Eggs_1 = ifelse(is.na(Eggs_1) & Eggs_2 == 2, 2, Eggs_1), 
         Notes = ifelse(!is.na(Notes), paste0(DateTime, ": ", Notes, ". "), ""), 
         Notes = paste0(Notes, collapse = "")) %>% 
  filter(nn == max(nn)) %>% 
  dplyr::select(-c(DateTime, Eggs, Chicks, nn, Status)) %>% 
  rename("Status" = "Status2")

failed_eggs <- eggs %>% 
  filter(Status == "Failed") %>%
  mutate(across(Est_TranspondDate5:Est_FledgeDate, ~NA),
         Status = "Failed-eggs",
         Comments = str_squish(Comments))

eggs <- eggs %>%
  filter(Status != "Failed")
```

### Nests with chicks
```{r chicks}
chicks <- nests %>% 
  filter(!Status %in% "Eggs") %>% 
  filter(!FullID %in% failed_eggs$FullID) %>% 
  group_by(FullID) %>% 
  mutate(HatchDate = min(DateTime), .after = Est_HatchDate,
         Est_TranspondDate5 = HatchDate + 35,
         Est_TranspondDate6 = HatchDate + 42,
         Est_FledgeDate = HatchDate + 56, 
         FledgeDate = ifelse(any(Status =="Fledged"), 
                             as.character(max(DateTime)), NA), 
         FledgeDate = as.Date(FledgeDate), 
         UpliftDate = ifelse(Status == "Uplifted", as.character(DateTime), NA),
         UpliftDate = as.Date(UpliftDate)) %>%
  fill("UpliftDate" ,.direction = "downup") %>% 
  dplyr::select(NestYear, FullID, DateTime, `Nest ID`, Status, Est_LayDate:UpliftDate, 
                Eggs, Chicks, NLaid, NHatched, Notes) %>% 
  #distinct(across(c(FullID, Status:Chicks)), .keep_all = T) %>%
  arrange(NestYear, `Nest ID`, DateTime) %>% 
  mutate(Chicks_1 = lag(as.numeric(Chicks)),
         Chicks_2 = as.numeric(Chicks),
         diffchicks = as.numeric(Chicks) - lag(as.numeric(Chicks)), 
         Comments = "", 
         Comments = ifelse(Status != "Fledged" & diffchicks < 0, 
                           paste0(diffchicks, " chicks on ", DateTime, ". "), NA),
         Comments = replace_na(Comments, ""),
         Comments = ifelse(Status == "Fledged" , 
                           paste0(Comments, "Fledged on ", DateTime, "."),
                           Comments), 
         Comments = ifelse(Status == "Failed" , 
                           paste0(Comments, "Failed (chicks) on ", DateTime, "."),
                           Comments), 
         Comments = ifelse(Status == "Uplifted" , 
                           paste0(Comments, "Uplifted chicks on ", DateTime, "."),
                           Comments), 
         Comments = paste(Comments, collapse = " "),
         Status2 = ifelse(any(Status == "Fledged"), "Fledged", Status),
         Status2 = ifelse(any(Status == "Failed"), "Failed", Status2),
         Status2 = ifelse(any(Status =="Uplifted"), "Uplifted", Status2),
         nn = row_number(), 
         Chicks_1 = ifelse(is.na(Chicks_1) & Chicks_2 == 2, 2, Chicks_1),
         Chicks_1 = ifelse(is.na(Chicks_1) & Chicks_2 == 1, 1, Chicks_1),
         Notes = ifelse(!is.na(Notes), paste0(DateTime, ": ", Notes, ". "), ""), 
         Notes = paste0(Notes, collapse = "")) %>% 
  filter(nn == max(nn)) %>% 
  mutate(Chicks_2 = ifelse(Status2 == "Failed", 0, Chicks_2), 
         Status2 = ifelse(FullID %in% failed_nests$FullID & Status2 == "Uplifted", "Uplifted-failed", Status2)) %>% 
  dplyr::select(-c(DateTime, Eggs, Chicks, nn, Status)) %>% 
  rename("Status" = "Status2") %>% 
  distinct()

# If failed at egg stage, remove
failed_chick <- chicks %>% 
  filter(Status == "Failed" | Status == "Uplifted-failed") %>%
  filter(!FullID %in% failed_eggs$FullID) %>%
  mutate(across(Est_TranspondDate5:Est_FledgeDate, ~NA),
         Status = "Failed-chicks",
         Comments = str_squish(Comments))

# If chicks uplifted (but did not fail)
uplifted_chick <- chicks %>%
  filter(Status == "Uplifted")

# Only successful chicks
chicks <- chicks %>% 
  filter(Status != "Failed" , Status != "Uplifted-failed", Status != "Uplifted")

#failed_nests %>% filter(!FullID %in% c(failed_eggs$FullID, failed_chick$FullID))

# Checking chicks without egg record
xx <- chicks %>% filter(!FullID %in% eggs$FullID) %>% 
  unite("Comments", c(Comments, Notes), sep = " ")

```

### Eggs + Chicks + Totals
```{r ect}

combo_nests <- eggs %>% 
  full_join(chicks, by = c("FullID"), suffix = c("", "x")) %>% 
  group_by(FullID) %>% 
  mutate(HatchDate = HatchDatex, 
         Status = ifelse(is.na(Statusx), Status, Statusx)) %>%  
  unite("Comments", c(Comments, Commentsx, Notes, Notesx), sep = " ") %>% 
  #NLaid = pmax(Eggs_1, Eggs_2, na.rm = T), 
  #NHatched = pmax(Chicks_1, Chicks_2, na.rm = T)) %>% 
  dplyr::select(c(NestYear, `Nest ID`, Status, Est_LayDate, Est_HatchDate, HatchDate, UpliftDate, Est_FledgeDate, FledgeDate, NLaid, diffeggs, NHatched, diffchicks, Comments)) %>%
  filter(!is.na(NestYear)) %>%
  bind_rows(xx) %>%
  mutate(Comments = str_squish(str_remove(Comments, "NA")), 
         Chicks_2 = ifelse(Status != "Chicks", NA, NHatched)) %>% # THIS MAY NOT ALWAYS HOLD TRUE
  arrange(NestYear, `Nest ID`)

failed_all <- rbind(failed_eggs, failed_chick, uplifted_chick) %>% 
  unite("Comments", c(Comments, Notes), sep = " ") %>% 
  select(names(combo_nests))

combo_nests <- combo_nests %>%
  filter(!FullID %in% failed_all$FullID) %>%
  bind_rows(failed_all)

```

# TOTALS
# CHICKS FLEDGED MAY BE HIGHER THAN TRUE, CANT FIGURE OUT TO DETERMINE FLEDGING IF ONE 
# CHICK DIES OVER THE SEASON AND ONLY ONE CHICK DIES. RIGHT NOW, CONSIDERED AS TOTAL HATCHED I.E. 2 NOT 1
```{r totals}
ccc <- unique(combo_nests$NestYear)

tots <- lapply(ccc, function(cc) {
  
  fn <- failed_all[failed_all$NestYear == cc,]
  cn <- combo_nests[combo_nests$NestYear == cc,]
  fl <- cn[cn$Status == "Fledged",]
  
  # Chicks per pair not being calculated correctly. 
  cn %>% 
    ungroup() %>%
    summarise(Total_nests = nrow(cn), 
              Nests_failed = nrow(fn[fn$Status != "Uplifted",]),
              Nests_uplifted = nrow(cn[cn$Status == "Uplifted" | cn$Status == "Uplifted-failed",]),
              Nest_successrate = (Total_nests-Nests_failed)/Total_nests, 
              Eggs_laid = sum(NLaid, na.rm = T),
              Chicks_hatched = sum(NHatched, na.rm = T), 
              Chicks_fledged = sum(fl$NHatched, na.rm = T), 
              Chicks_perpair = Chicks_fledged/Total_nests, 
              Chicks_peradult = Chicks_fledged/(Total_nests*2)) 
})

```

### Adding parent and chick marking data to dataframes
```{r parentid}

#############################################
##### START HERE. COMPARE PAIRS ACROSS YEARS
############################################
birdid_all <- birdid %>%
  mutate(NestYear = ifelse(month(DateTime_marking) > 7, 
                           year(DateTime_marking), 
                           year(DateTime_marking)-1),
         FullID = ifelse(!is.na(`Nest ID_marking`), 
                         paste0(NestYear, `Nest ID_marking`), NA)) %>% 
  group_by(FullID) %>%
  #filter(FullID %in% combo_nests$FullID) %>% 
  dplyr::select(c(NestYear, FullID, `Bird ID`, `Age_marking`, Sex)) %>% 
  group_by(FullID, Age_marking) %>% 
  arrange(FullID, Age_marking, Sex) %>%
  mutate(n = row_number()) %>% 
  #  unite(nn, Age_marking, n, sep = "", remove = FALSE)  %>%
  ungroup() %>%
  mutate(Age_current = ifelse(Age_marking == "Adult", "Adult", 0), 
         Age_current = ifelse(Age_current == 0 & Age_marking == "Chick" & NestYear !=yr, 
                              yr-NestYear, Age_current), .after = Age_marking)

birdid_chicks <- birdid_all %>% 
  filter(#Year == yr, 
    Age_marking %in% "Chick")

birdid_adults <- birdid_all %>% 
  filter(Age_marking %in% "Adult")

birdid_all_f <- birdid_all %>%
  #filter(!is.na(FullID)) %>%# remove birds (chicks) with no nest ID
  filter(FullID != "2022DUMMY" | is.na(FullID))

# Number of visits
nvisits <- nests %>% 
  group_by(FullID) %>% 
  summarise(nvisits = max(row_number()))

# Parents
parents <- nests %>%
  mutate(NestYear = ifelse(month(DateTime) > 7, 
                           year(DateTime), 
                           year(DateTime)-1),
         FullID = ifelse(!is.na(`Nest ID`), 
                         paste0(NestYear, `Nest ID`), NA)) %>% 
  group_by(FullID) %>%
  dplyr::select(NestYear, FullID, `Adult 1`, `Adult 2`, DateTime) %>%
  pivot_longer(cols = 3:4, names_to = "Ind", values_to = "ID") %>%
  filter(!is.na(ID)) %>%
  group_by(FullID, ID) %>%
  mutate(lastdate = max(DateTime), 
         nseen = n(), 
         Ind = str_replace_all(Ind, "\\s\\d", "")) %>%
  dplyr::select(-DateTime) %>%
  distinct() 

parents_compare <- parents %>%
  left_join(birdid_all_f, by = c("ID" = "Bird ID"), suffix = c("", "_marking")) %>%
  #mutate(Ind = ifelse(Sex == "Female" | Sex == "Unknown", "Adult1", "Adult2")) %>%
  #mutate(nn_marking = str_replace_all(nn, "\\d", "")) %>%
  dplyr::select(-c(FullID_marking, Ind)) %>%
  arrange(FullID)

juves <- filter(parents_compare, Age_current == 1)

# Trying to identify which are new pairs. no idea how
parents_years <- parents_compare %>%
  filter(Age_current != 1) %>% # no juves
  group_by(ID) %>%
  arrange(ID) %>%
  mutate(NestID = str_replace_all(FullID, "^\\d{4}", ""),
         diffnest = ifelse(n_distinct(NestID) > 1, "diff", "same"), 
         diffnest = ifelse(row_number() == 1, "first_year", diffnest)) %>%
  ungroup() %>%
  group_by(NestID) %>%
  mutate(diffpair = ifelse(n_distinct(ID) > 2, "diff", "same"),# THIS ISNT RIGHT, FIX!
         diffpair = ifelse(diffnest == "first_year", "first_year", diffpair)) %>%
  arrange(FullID) %>%
  select(-c(NestYear, NestID))

clipr::write_clip(parents_years)

# Birds age 2

```

```{r}
combo_nests_current <- combo_nests %>%
  filter(NestYear == yr)

# Current parents
nests_outcome <- parents %>%
  left_join(birdid_all_f, by = c('ID' = "Bird ID"), suffix = c("", "x"))

# Current chicks
current_chicks <- birdid_chicks %>%
  filter(NestYear == yr, 
         !is.na(FullID)) %>%
  group_by(FullID) %>% 
  mutate(n = row_number(), 
         nn = paste0("Chick", n)) %>%
  select(c("FullID", "Bird ID", "nn")) %>%
  pivot_wider(names_from = nn, values_from = "Bird ID")

# Resights this year
resights_current <- filter(nests_outcome, Age_current == 1)

# Combining parents + chicks + nest info
nests_outcome <- nests_outcome %>%
  filter(Age_current != 1) %>% 
  group_by(FullID) %>%
  arrange(FullID, Sex) %>%
  mutate(n = row_number(), 
         n = ifelse(n == 2 & Sex == "Female", max(n), n), 
         n = ifelse(Sex == "Male", 2, n), 
         n = ifelse(duplicated(n) | duplicated(n, fromLast = TRUE) &
                      row_number() > 2, n + 1, n)) %>%
  unite(nn, Ind, n, sep = "", remove = FALSE) %>% 
  select(-c(NestYear, NestYearx, FullIDx, Age_marking, 
            Age_current, Sex, n, lastdate, nseen, Ind)) %>%
  pivot_wider(names_from = nn, values_from = ID) %>% 
  right_join(combo_nests_current, by = "FullID") %>%
  left_join(current_chicks, by = "FullID") %>%
  left_join(nvisits, by = c("FullID")) %>% 
  arrange(FullID) %>% 
  ungroup() %>% 
  rename("NFledged" = "Chicks_2", 
         'NestID' = `Nest ID`,
         "Nvisits" = "nvisits", 
         "SeasonID" = "FullID") %>% 
  rename_with(~str_c(., "ID"), starts_with("Chick")) %>% 
  rename_with(~str_c(., "ID"), starts_with("Adult")) %>% 
  mutate_if(is.Date, format, format = "%d/%m/%Y") %>% 
  mutate_all(as.character) %>% 
  mutate(EC1Fate = NA, EC2Fate = NA, EC1Intervention = NA, EC2Intervention = NA, .before = Comments) %>% 
  mutate(across(ends_with(c("1ID", "2ID")), replace_na, "UM")) %>%
  mutate(NFledged = ifelse(Chick1ID != "UM" & Chick2ID != "UM", 2, NFledged), 
         NFledged = ifelse(Status == "Fledged" & is.na(NFledged), NHatched, NFledged)) %>%
  mutate(EC1Fate = ifelse(Status == "Fledged" & NFledged <= 2, "Fledged", EC1Fate), 
         EC2Fate = ifelse(Status == "Fledged" & NFledged == 2, "Fledged", EC2Fate), 
         Comments = str_squish(Comments)) %>%
  mutate(across(Est_LayDate:FledgeDate, ~ dmy(.))) %>%
  select(NestYear, SeasonID, NestID, starts_with("Adult"), Status, NLaid:diffchicks, NFledged, EC1Fate:EC2Intervention, Chick1ID:Chick2ID, Est_LayDate:FledgeDate, Comments, Nvisits)
```

```{r}
openxlsx::write.xlsx(nests_outcome, paste0("./../ALL_DATA/Data/2024-2025/", "BreedingSeason_", yr, "_finalsummary.xlsx"), 
                     colNames = TRUE, rowNames = FALSE, append = FALSE)

#write.csv(nests_outcome, paste0("./../ALL_DATA/Data/BreedingSeason_", yr, "_finalsummary.csv"), row.names = FALSE)

nests_outcome_2024 <- read.xlsx(paste0("./../ALL_DATA/Data/2024-2025/", "BreedingSeason_", yr, "_finalsummary_edited.xlsm"))
nests_outcome_2023 <- read.xlsx(paste0("./../ALL_DATA/Data/2023-2024/", "BreedingSeason_2023_finalsummary_edited.xlsm"))
nests_outcome_2022 <- read.xlsx(paste0("./../ALL_DATA/Data/2022-2023/", "BreedingSeason_2022_finalsummary_edited.xlsm"))

```


### Getting information about the moult
```{r moult}
moult <- monitor %>%
  filter(`Nest activity` == "Moulting") %>%
  mutate(.before = 1, NestYear = ifelse(month(DateTime) > 7, 
                                        year(DateTime), 
                                        year(DateTime)-1),
         FullID = ifelse(!is.na(`Nest ID`), 
                         paste0(NestYear, `Nest ID`), NA))

length(unique(moult$`Adult 1`))
length(unique(moult$`Nest ID`))

ccc <- unique(moult$NestYear)

markedmoult <- lapply(ccc, function(ccc) {
  moult %>%
    filter(NestYear == ccc) %>% 
    select(NestYear, FullID, `Nest ID`, `Adult 1`, `Adult 2`, `Adult 3`, `Adult 4`) %>% 
    pivot_longer(c(`Adult 1`, `Adult 2`, `Adult 3`, `Adult 4`), names_to = "n", values_to = "AdultID") %>% 
    filter(!is.na(AdultID)) %>% 
    select(-n) %>% 
    distinct() %>%
    left_join(birdid_all, by = c("AdultID" = "Bird ID"), suffix = c("", "x"))
})

notmoult <- lapply(markedmoult, function(markedmoult) {
  xx <- unique(markedmoult$NestYear)
  birdid_all %>% 
    filter(NestYear <= xx, 
           !`Bird ID` %in% markedmoult$AdultID) %>% 
    filter(!Age_current %in% c("0", "1", "Chick"))
})

notmoult_juv <- lapply(markedmoult, function(markedmoult) {
  xx <- unique(markedmoult$NestYear)
  birdid_all %>% 
    filter(NestYear <= xx, 
           !`Bird ID` %in% markedmoult$AdultID) %>% 
    filter(Age_current == "1")
})

tmoult <- lapply(markedmoult, function(x){nrow(x)})
tnotmoult <- lapply(notmoult, function(x){nrow(x)})


# Number of 2-3 year olds that were also breeders
xxx <- filter(markedmoult[[2]], Age_current %in% c(2, 3))
ccc <- filter(parents, NestYear == 2024)
table(ccc$ID %in% xxx$AdultID)

# Number of breeding adults marked resighted at moult
xxx <- filter(markedmoult[[2]], Age_current == "Adult")
ccc <- filter(parents, NestYear == 2024)
table(ccc$ID %in% xxx$AdultID)

# Number of juveniles
xxx <- filter(markedmoult[[2]], Age_current == 1)

# Number of breeding adults marked resighted at breeding
ccc <- filter(parents, NestYear == 2024)
table(birdid_adults$`Bird ID` %in% ccc$ID)

```

### RESIGHTS
```{r resight}
# Resights from birdid
# resight_birdid <- birdid %>% 
#   select(`Bird ID`, Sex, DateTime_resighting, `Nest ID_resighting`, `Age_resighting`:`Bill length_resighting`) %>%
#   filter(!is.na(Status_resighting))

cc <- c("Adult 1", "Adult 2", "Adult 3", "Adult 4", 
        "Chick 1 ID", "Chick 2 ID", "Chick 3 ID", "Chick 4 ID")

# Resights from monitoring
resight <- monitor %>%
  select(DateTime, `Nest ID`, `Nest activity`, `Number of adults`, all_of(cc)) %>% 
  #filter(DateTime >= start & DateTime <= end) %>% # THIS SEASON ONLY
  pivot_longer(all_of(cc), names_to = "n", values_to = "BirdID") %>% 
  group_by(BirdID) %>% 
  filter(!is.na(BirdID)) %>% 
  mutate(NestYear = ifelse(month(DateTime) > 7, 
                           year(DateTime), 
                           year(DateTime)-1), .before = 1) %>%
  mutate(Age_resight = str_replace_all(n, " ID", ""),
         Age_resight = str_replace_all(n, "\\s\\d", "")) 
names(resight) <- c("NestYear_resight", "Datetime_resight", "NestID_resight", 
                    "Status_resight", "n_adults_resight", "n", "BirdID", "Age_resight")

# Join bird data with resight
resight <- birdid_all %>%
  rename("BirdID" = "Bird ID") %>%
  left_join(resight, by = "BirdID", suffix = c("", ".x")) %>%
  select(-c(n.x, n, n_adults_resight)) %>%
  mutate(Age_resight = str_replace_all(Age_resight, pattern = "Chick ID", 
                                       replacement = "Chick"), 
         Status_resight = case_when(
           Status_resight == "Eggs/Chicks present" ~ "Breeding",
           Status_resight == "Loafing adult(s)" ~ "Loafing",
           TRUE ~ Status_resight
         ), 
         # Identify chick resights on nest
         Status_resight = ifelse(NestYear == NestYear_resight & 
                                   Age_marking == "Chick", "Chick in nest", 
                                 Status_resight)) %>%
  group_by(BirdID) %>%
  mutate(n = n(), 
         n = ifelse(all(is.na(Datetime_resight)), 0, n))

# Weird resights
resight_weird <- filter(resight, Status_resight %in% c("Breeding", "FAILED"))  %>% group_by(BirdID) %>%
  mutate(n = n()) %>%
  group_by(BirdID, NestYear_resight) %>%
  mutate(n_year = n()) %>%
  select(-Datetime_resight) %>%
  distinct() %>%
  filter(Age_current %in% c("1", "0"))


# Resightings during breeding season
resight_breeding <- filter(resight, Status_resight %in% c("Breeding", "FAILED"), 
                           !Age_current %in% c("1", "0"))  %>% 
  group_by(BirdID) %>%
  mutate(n = n()) %>%
  group_by(BirdID, NestYear_resight) %>%
  mutate(n_year = n()) %>%
  select(-Datetime_resight) %>%
  distinct() #%>%
#split(.$NestYear_resight)

# Resightings during moult only
resight_moult <- filter(resight, Status_resight == "Moulting") %>% 
  group_by(BirdID) %>%
  mutate(n = n()) %>%
  group_by(BirdID, NestYear_resight) %>%
  mutate(n_year = n()) %>%
  select(-Datetime_resight) %>%
  distinct()# %>%
#split(.$NestYear_resight)

# Resightings LOAFING but no seen BREEDING OR MOULTING)
resight_loaf <- filter(resight, Status_resight == "Loafing") %>% 
  group_by(BirdID) %>%
  mutate(n = n()) %>%
  group_by(BirdID, NestYear_resight) %>%
  mutate(n_year = n()) %>%
  select(-Datetime_resight) %>%
  distinct() #%>%
#split(.$NestYear_resight)

# No resightings
resight_no <- filter(resight, is.na(Status_resight)) %>% 
  group_by(BirdID) %>%
  filter(Age_current != 0, !is.na(Age_current))

# Summary tables
## All marked birds
sum_birdid <- birdid_all %>%
  group_by(NestYear) %>%
  summarise(total_marked_year = sum(!`Bird ID` %in% c("P41704", "UM"), na.rm = TRUE), 
            total_chicks_marked = sum(Age_marking == "Chick", na.rm = TRUE), 
            total_adults_marked = sum(Age_marking %in% c("Adult", "Juvenile"), 
                                      na.rm = TRUE)) %>%
  mutate(cumsum_total_marked = cumsum(total_marked_year),
         cumsum_adults_marked = cumsum(total_adults_marked), 
         total_juveniles_marked = lag(total_chicks_marked),
         total_juveniles_marked = replace_na(total_juveniles_marked, 0),
         cumsum_juveniles_marked = cumsum(total_juveniles_marked),
         total_breeding_age_marked = cumsum_adults_marked + lag(cumsum_juveniles_marked))

## Breeders
resight_df <- resight_breeding %>%
  group_by(NestYear_resight) %>%
  mutate(NestID = sub("^.{4}", "", FullID), .after = 1) %>%
  mutate(Age_resight = NestYear_resight - NestYear, 
         Age_resight = ifelse(Age_marking == "Adult", "Adult", Age_resight)) %>%
  summarise(resight_1 = sum(Age_resight == "1", na.rm = TRUE), 
            resight_2 = sum(Age_resight == "2", na.rm = TRUE), 
            resight_3 = sum(Age_resight == "3", na.rm = TRUE), 
            # Total birds that are not 1 or 2 upon resight
            resight_adults = sum(!Age_resight %in% c("1", "2", "3"), na.rm = TRUE), 
            resight_total = n(), 
            diff_nestbox = sum(NestID != NestID_resight, na.rm = TRUE), 
            same_nestbox = sum(NestID == NestID_resight, na.rm = TRUE)) %>%
  full_join(sum_birdid, by = c("NestYear_resight" = "NestYear")) %>%
  select(-cumsum_juveniles_marked) %>%
  arrange(NestYear_resight) %>%
  relocate(total_marked_year:total_adults_marked, .after = 1) %>%
  mutate(.after = "resight_total", 
         # 2 yr old Recruitment rate 
         # 2 year olds breeding from the marked chicks 2 years ago, i.e., cohort
         `percent_resight_2/cohort` = 
           round((resight_2/lag(total_juveniles_marked))*100, 1), 
         # 3 yr old Recruitment rate 
         # 3 year olds breeding from the marked chicks 2 years ago, i.e., cohort
         `percent_resight_3/cohort` = 
           round((resight_3/lag(lag(total_juveniles_marked)))*100, 1), 
         # Breeding rate
         # Number of resighted breeders / breeding population of birds
         `percent_resight_total/cumsum_breeding_age` = 
           round((resight_total/total_breeding_age_marked)*100, 1))

## Moulters
moult_df <- resight_moult %>%





```  

### Reading in cleaned yearly summary of breeding
```{r cleanedsum}
breeding <- read_excel("./../ALL_DATA/Data/2024-2025/BreedingSeason_2024_finalsummary_edited.xlsx")
```

################################################################################
### Weights
#### THERE ARE PROBLEMS HERE THAT NEED FIXING
```{r weights}

weight_sum <- birdid %>%
  mutate(NestYear = ifelse(month(DateTime_marking) > 7, 
                           year(DateTime_marking), 
                           year(DateTime_marking)-1),
         FullID = ifelse(!is.na(`Nest ID_marking`), 
                         paste0(NestYear, `Nest ID_marking`), NA)) %>% 
  group_by(NestYear, Age_marking) %>%
  summarise(min_wg = min(Weight_marking, na.rm = TRUE), 
            mean_wg = mean(Weight_marking, na.rm = TRUE), 
            max_wg = max(Weight_marking, na.rm = TRUE)) %>%
  filter(NestYear != 2021, Age_marking %in% c("Chick", "Adult"))

weights_time <- nests %>%
  select(NestYear, FullID, DateTime, Week, starts_with("Chick ")) %>%
  filter(!is.na(`Chick 1 weight`) | !is.na(`Chick 2 weight`)) %>%
  left_join(combo_nests[c(1, 2, 4, 7, 9:10)], by = c("FullID", "NestYear")) %>%
  pivot_longer(
    cols = c("Chick 1 ID", "Chick 1 weight", "Chick 1 status", "Chick 2 ID", "Chick 2 weight", "Chick 2 status"),
    names_to = c("chick_number", ".value"),
    names_pattern = "Chick (\\d+) (.*)") %>%
  mutate(Chick = paste(FullID, chick_number, sep = "_")) %>%
  mutate(Week_f = factor(Week, levels = c(40:58, 1:10)))

ggplot(data = weights_time, aes(x = Week_f, y = weight, color = NestYear, group = FullID)) +
  geom_point() +  # Points with transparency for clarity
  geom_line(alpha = 0.7) +  # Line connecting the points
  labs(
    title = "Weight of Chicks Over Time",
    x = "Week",
    y = "Weight (grams)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    panel.grid.major = element_line(color = "gray80", size = 0.5),  # Lighter grid lines
    panel.grid.minor = element_line(color = "gray90", size = 0.25),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  # Center title
    axis.title = element_text(size = 12),  # Axis titles
    axis.text = element_text(size = 10)  # Axis text
  ) +
  guides(color = guide_legend(title = "Nest Year"), shape = guide_legend(title = "Nest Year"))


weights_age <- weights_time %>%
  mutate(Days_old = DateTime - HatchDate, 
         Weeks_old = as.numeric(Days_old/7)) %>%
  filter(Weeks_old <= 10)  %>% # no rehab chicks
  arrange(FullID, chick_number)

weights_age_sequence <- weights_age %>%
  group_by(Chick) %>%
  mutate(n = n()) %>%
  filter(n > 2) #more than two points per penguin


ggplot(data = weights_age_sequence, aes(x = Days_old, y = weight, color = factor(NestYear), group = Chick)) +
  geom_point() +  # Points with transparency for clarity
  #geom_line(alpha = 0.7) +  # Line connecting the points
  geom_smooth(method = "loess", se = FALSE, alpha = 0.5) + 
  labs(
    title = "Weight of Chicks By Age",
    x = "Days old",
    y = "Weight (grams)"
  ) +
  scale_color_manual(values = c("maroon", "gold")) +  # Manual color scale for NestYear
  theme_minimal() +
  theme(
    panel.grid.major = element_line(color = "gray80", size = 0.5),  # Lighter grid lines
    panel.grid.minor = element_line(color = "gray90", size = 0.25),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  # Center title
    axis.title = element_text(size = 12),  # Axis titles
    axis.text = element_text(size = 10)  # Axis text
  ) +
  guides(color = guide_legend(title = "Nest Year"), shape = guide_legend(title = "Nest Year"))

# mutate(Underweight = ifelse(Weight <= 700 & days_hatch >= 42, "Concern", "Ok"), 
#        Underweight = ifelse(Weight <= 600 & days_hatch >= 42, "Intervene", Underweight)) %>% 

weights_summary <- weights_age_sequence %>%
  group_by(Days_old, NestYear) %>%
  summarise(
    mean_weight = mean(weight, na.rm = TRUE),
    sd_weight = sd(weight, na.rm = TRUE))

# Plot the mean and SD of weights by age per year
ggplot(weights_summary, aes(x = Days_old, y = mean_weight, color = factor(NestYear))) +
  # Add mean line
  #geom_line(size = 1.2) + 
  # Add shaded SD ribbon
  # geom_ribbon(aes(ymin = mean_weight - sd_weight, ymax = mean_weight + sd_weight, fill = factor(NestYear)), 
  #             alpha = 0.2) + 
  geom_smooth(method = "loess", aes(color = factor(NestYear)), se = TRUE, alpha = 0.2) +
  labs(
    title = "Mean and Standard Deviation of Chick Weights By Age",
    x = "Days old",
    y = "Weight (grams)"
  ) +
  scale_color_manual(values = c("maroon", "gold")) +  # Custom color for NestYear
  scale_fill_manual(values = c("maroon", "gold")) +  # Custom fill color for SD ribbon
  theme_minimal() +
  theme(
    panel.grid.major = element_line(color = "gray80", size = 0.5),
    panel.grid.minor = element_line(color = "gray90", size = 0.25),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  ) +
  guides(color = guide_legend(title = "Nest Year"), fill = guide_legend(title = "Nest Year"))


```

```{r ecfateplot}
# ecfate <- read_excel("nests_ecfate_18112022.xlsx")
# ecfate$code <- as.factor(ecfate$code)
# #ccord <- ecfate %>% filter(!is.na(Lat))
# #coordinates(ccord) <- ~Lat+Long
# 
# library(leaflet)
# pal <- colorFactor(c("yellow", "blue", "purple", "orange", "red"), ecfate$code)
# lab <- as.character(ecfate$code)
# 
# x <- leaflet() %>% 
#   #addCircles(lng = ~Long, lat = ~Lat) %>% 
#   addTiles('http://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}',
#            options = providerTileOptions(noWrap = TRUE), group = "World Imagery") %>%
#   # addTiles('http://server.arcgisonline.com/ArcGIS/rest/services/Reference/World_Boundaries_and_Places/Mapserver/tile/{z}/{y}/{x}',
#   #          options = providerTileOptions(noWrap = TRUE),group = "Labels") %>% 
#   addCircleMarkers(data = ecfate, lat = ~Lat, lng = ~Long,
#                    radius = 3,
#                    color = ~pal(ecfate$code),
#                    stroke = FALSE, fillOpacity = 1) %>%
#   leaflet::addLegend(pal = pal, values = lab, opacity = 1, position = "bottomleft") %>%
#   fitBounds(173.00275,-43.871,173.015,-43.866)
# 
# library(mapview)
# library(htmlwidgets)
# mapshot(x, file = "~/map_activefailednests.png")
# saveWidget(x, selfcontained = T, file = "~/map_activefailednests.html")
# 
# resfactor <- 3
# png(filename=x, res = 72*resfactor, height=640*resfactor, width=640*resfactor)
```

```{r}
# ggplot(data = allstats2[allstats2$name != "nest_monitored",]) +
#   geom_line(aes(x = week, y = count, group = name, colour = name), size = 1) +
#   scale_colour_manual(values = c("darkgreen", "orange", "deepskyblue", "red", "purple", "magenta")) +
#   geom_point(aes(x = week, y = count, group = name, fill = name)) +
#   scale_fill_manual(values = c("darkgreen", "orange", "deepskyblue", "red", "purple", "magenta")) +
#   theme_minimal() +
#   theme(axis.title = element_blank(), 
#         legend.title = element_blank(), 
#         axis.text.y = element_text(size = 14), 
#         axis.text.x = element_text(angle = 45, size = 11, hjust = .9),
#         legend.text = element_text(size = 14), 
#         legend.position = "top")

```

