---
title: "Pohatu Penguins Monitoring Data Analysis"
author: "Rachel Hickcox"
date: "2022"
email: "rphickcox@gmail.com"
editor_options: 
  chunk_output_type: console
---

### Load packages
```{r pkg, eval=TRUE, message=FALSE, warning=FALSE, cache=FALSE}
pkgs <- c("rgdal", "rgeos", "raster", "knitr", "kableExtra", "broom", 
          "readxl", "flextable", "terra", "googlesheets4", "googledrive", "lubridate", "tidyverse", "openxlsx")
new.packages <- pkgs[!(pkgs %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
invisible(lapply(pkgs, library, character.only = TRUE))
rm(list = c("pkgs", "new.packages"))
options(scipen = 999)
```

### Connecting to Google Drive
```{r googledrive}
drive_auth(email = "pohatumonitoring@gmail.com")

drive_download(file = "https://docs.google.com/spreadsheets/d/1mEcD3r8sAauUH_rE5dDMkvpPlYNVqrEXawA0CYAg34E", 
               overwrite = TRUE, 
               path = "./../ALL_DATA/Data/Monitoring.xlsx")
monitor <- read_excel("./../ALL_DATA/Data/Monitoring.xlsx")

drive_download(file = "https://docs.google.com/spreadsheets/d/1qh6zAXgVokfdx4WjjSls8qh4tAfEOL-bO3xg3CvRY44", 
               overwrite = TRUE,
               path = "./../ALL_DATA/Data/Nest ID.xlsx")
nestid <- read_excel("./../ALL_DATA/Data/Nest ID.xlsx")

nestid2 <- nestid %>% 
  separate(col = Location, into = c("Lat", "Lon"), sep = ",", remove = FALSE) %>% 
  mutate(Lat = ifelse(str_detect(`Nest ID`, "^DUD"), NA, Lat), 
         Lon = ifelse(str_detect(`Nest ID`, "^DUD"), NA, Lon)) %>% 
  arrange(`Nest ID`)
write.csv(nestid2, "./../ALL_DATA/Data/Nest ID.csv")

drive_download(file = "https://docs.google.com/spreadsheets/d/16c4c5nXbz_PFf7iyN2DG7fExsi4P5uP-NSYAbCDX1rc", 
               overwrite = TRUE, 
               path = "./../ALL_DATA/Bird ID.xlsx")
birdid <- read_excel("./../ALL_DATA/Bird ID.xlsx")
```

### Setup
```{r setup}
# Dates
tdt <- floor_date(today(), "weeks", week_start = 1) # lubridate start of week
tdt_d <- format(tdt, "%d-%m-%Y") # character today's start of week date 
tdt_s <- as.numeric(str_replace_all(as.character(tdt), pattern = "-", "")) # string
yr <- ifelse(month(today()) > 8, year(today()), year(today())-1) # yr
start <- floor_date(as.Date(paste0("01-08-", yr), "%d-%m-%Y"), "weeks", week_start = 1) # start date
end <- as.Date(paste0("01-09-", yr + 1), "%d-%m-%Y")
non_br <- as.Date(paste0("01-04-", yr + 1), "%d-%m-%Y")
dates_df <- seq(start, today(), 7)
```

### CHOOSING NEST YEAR
```{r ny}
yr <- ifelse(month(today()) > 8, year(today()), year(today())-1) # yr
#yr <- 2022
```


### Nests summary
```{r nests}
# Nest coords 
nestid_coord <- nestid %>%
  tidyr::separate(Location, into = c("Lat", "Long"), ",") %>%
  dplyr::select(`Nest ID`, Lat, Long) %>%
  mutate(Lat = as.numeric(Lat), Long = as.numeric(Long))

nests <- monitor %>%
  mutate(NestYear = ifelse(month(DateTime) > 7, year(DateTime), year(DateTime)-1),
         FullID = paste0(NestYear, `Nest ID`), 
         Eggs = ifelse(is.na(Eggs), 0, as.numeric(Eggs)), 
         Chicks = ifelse(is.na(Chicks), 0, as.numeric(Chicks))) %>%  
  group_by(FullID) %>%
  arrange(`Nest ID`, DateTime) %>%
  mutate(n = row_number()) %>%
  mutate(n1 = ifelse(`Nest activity` == "Eggs/Chicks present", n, NA)) %>%
  filter(n >= min(n1, na.rm = TRUE)-1 | n == max(n1, na.rm = TRUE)+1) %>%
  mutate(Date_last = lag(DateTime), .before = DateTime) %>% 
  filter(`Nest activity` == "Eggs/Chicks present" | 
           `Nest activity` == "FAILED" | 
           `Nest activity` == "Empty") %>%
  mutate(`Nest activity` = ifelse(Interaction == "Uplifted", 
                                  "Uplifted",`Nest activity`)) %>% 
  mutate(.after = 2,
         DateTime = as.Date(DateTime),
         Week = ifelse(year(DateTime) > yr, week(DateTime)+52, week(DateTime)),
         Date_last = difftime(as.Date(DateTime), as.Date(Date_last), units = "days"), 
         Est_LayDate = as.Date(min(DateTime, na.rm = TRUE))) %>%
  mutate(.after = Est_LayDate, Est_HatchDate = Est_LayDate + 35) %>% 
  dplyr::select(NestYear, FullID, `Nest ID`, Date_last:Est_HatchDate, `Nest activity`:`Adult 1`, 
                `Adult 2`, Eggs:`Chick 1 weight`, `Chick 2 ID`:`Chick 2 weight`,
                Notes, n, n1) %>%
  mutate(Status = ifelse(Eggs > 0, "Eggs", NA), 
         Status = ifelse(Chicks > 0, "Chicks", Status), 
         .before = 2) %>% 
  left_join(nestid_coord, by = "Nest ID") %>% 
  mutate(n2 = lag(Chicks)) %>% 
  group_by(FullID) %>% 
  mutate(`Nest activity` = ifelse(lag(`Nest activity`) == "FAILED" & 
                                    `Nest activity` == "FAILED", NA, `Nest activity`),
         Status = ifelse(is.na(`Nest activity`), NA, Status),
         Status = ifelse(is.na(n1) & n2 > 0, "Fledged", Status),
         Status = ifelse(`Nest activity` == "FAILED", "Failed", Status), 
         Status = ifelse(`Nest activity` == "Uplifted", `Nest activity`, Status),
         #if failed followed by empty, removing all empty rows (i.e., did not fledge)
         nn = ifelse(lag(`Nest activity`) == "FAILED" & 
                       `Nest activity` == "Empty", "R", NA),
         #if uplifted followed by empty, removing all empty rows (i.e., did not fledge)
         nn = ifelse(lag(`Nest activity`) == "Uplifted" & 
                       `Nest activity` == "Empty", "R", nn),
         #if row fledged but was previously uplifted, changing status to the previous status (i.e., did not fledge before uplift)
         Status = ifelse(Status == "Fledged" & 
                           lead(`Nest activity`) == "Uplifted", lag(Status), Status),
         nn = unlist(nn), 
         NHatched = ifelse(max(Chicks, na.rm = T) > 2, 2, max(Chicks, na.rm = T)), 
         NLaid = ifelse(NHatched == 2, 2, max(Eggs, na.rm = T))) %>% 
  filter(!is.na(Status), is.na(nn)) %>% 
  dplyr::select(-c(n, n1, n2, nn))
```

### Nests failed
```{r failed}
# Failed nests 
failed_nests <- nests %>%
  filter(Status == "Failed") %>% # | Status == "Uplifted") %>%
  #dplyr::select(NestYear, `Nest ID`, `Nest activity`, DateTime) %>% 
  dplyr::select(-c(Date_last, Week, `Nest activity`)) %>% 
  arrange(NestYear, `Nest ID`, DateTime) %>%
  group_by(FullID) %>% 
  filter(DateTime == min(DateTime))
#clipr::write_clip(failed_nests)
```

### Nests with eggs
```{r eggs}
eggs <- nests %>% 
  filter(Eggs != 0 & Status != "Chicks") %>% 
  dplyr::select(NestYear, DateTime, FullID, `Nest ID`, Status, Est_LayDate:Est_HatchDate, 
                Eggs, Chicks, NLaid, NHatched, Notes) %>% 
  distinct(across(NestYear:Chicks), .keep_all = T) %>%
  group_by(FullID) %>% 
  arrange(NestYear, `Nest ID`, DateTime) %>% 
  mutate(HatchDate = NA, .after = Est_HatchDate, 
         Est_TranspondDate5 = Est_HatchDate + 35,
         Est_TranspondDate6 = Est_HatchDate + 42,
         Est_FledgeDate = Est_HatchDate + 56, 
         Eggs_1 = lag(as.numeric(Eggs)),
         Eggs_2 = as.numeric(Eggs)) %>% 
  mutate(diffeggs = as.numeric(Eggs) - lag(as.numeric(Eggs)), .after = Eggs_2, 
         Comments = "", 
         Comments = ifelse(Status != "Failed" & diffeggs < 0, 
                           paste0(diffeggs, " eggs on ", DateTime, "."), NA), 
         Comments = replace_na(Comments, ""),
         Comments = ifelse(Status == "Failed" , 
                           paste0(Comments, "Failed (eggs) on ", DateTime, "."),
                           Comments), 
         Comments = paste(Comments, collapse = " "),
         Status2 = ifelse(any(Status =="Failed"), "Failed", Status),
         nn = row_number(), 
         Eggs_1 = ifelse(is.na(Eggs_1) & Eggs_2 == 2, 2, Eggs_1), 
         Notes = ifelse(!is.na(Notes), paste0(DateTime, ": ", Notes, ". "), ""), 
         Notes = paste0(Notes, collapse = "")) %>% 
  filter(nn == max(nn)) %>% 
  dplyr::select(-c(DateTime, Eggs, Chicks, nn, Status)) %>% 
  rename("Status" = "Status2")

failed_eggs <- eggs %>% 
  filter(Status == "Failed") %>%
  mutate(across(Est_TranspondDate5:Est_FledgeDate, ~NA),
         Status = "Failed-eggs",
         Comments = str_squish(Comments))

eggs <- eggs %>%
  filter(Status != "Failed")
```

### Nests with chicks
```{r chicks}
chicks <- nests %>% 
  filter(!Status %in% "Eggs") %>% 
  filter(!FullID %in% failed_eggs$FullID) %>% 
  group_by(FullID) %>% 
  mutate(HatchDate = min(DateTime), .after = Est_HatchDate,
         Est_TranspondDate5 = HatchDate + 35,
         Est_TranspondDate6 = HatchDate + 42,
         Est_FledgeDate = HatchDate + 56, 
         FledgeDate = ifelse(any(Status =="Fledged"), 
                             as.character(max(DateTime)), NA), 
         FledgeDate = as.Date(FledgeDate), 
         UpliftDate = ifelse(Status == "Uplifted", as.character(DateTime), NA),
         UpliftDate = as.Date(UpliftDate)) %>%
  fill("UpliftDate" ,.direction = "downup") %>% 
  dplyr::select(NestYear, FullID, DateTime, `Nest ID`, Status, Est_LayDate:UpliftDate, 
                Eggs, Chicks, NLaid, NHatched, Notes) %>% 
  #distinct(across(c(FullID, Status:Chicks)), .keep_all = T) %>%
  arrange(NestYear, `Nest ID`, DateTime) %>% 
  mutate(Chicks_1 = lag(as.numeric(Chicks)),
         Chicks_2 = as.numeric(Chicks),
         diffchicks = as.numeric(Chicks) - lag(as.numeric(Chicks)), 
         Comments = "", 
         Comments = ifelse(Status != "Fledged" & diffchicks < 0, 
                           paste0(diffchicks, " chicks on ", DateTime, ". "), NA),
         Comments = replace_na(Comments, ""),
         Comments = ifelse(Status == "Fledged" , 
                           paste0(Comments, "Fledged on ", DateTime, "."),
                           Comments), 
         Comments = ifelse(Status == "Failed" , 
                           paste0(Comments, "Failed (chicks) on ", DateTime, "."),
                           Comments), 
         Comments = ifelse(Status == "Uplifted" , 
                           paste0(Comments, "Uplifted chicks on ", DateTime, "."),
                           Comments), 
         Comments = paste(Comments, collapse = " "),
         Status2 = ifelse(any(Status == "Fledged"), "Fledged", Status),
         Status2 = ifelse(any(Status == "Failed"), "Failed", Status),
         Status2 = ifelse(any(Status =="Uplifted"), "Uplifted", Status2),
         nn = row_number(), 
         Chicks_1 = ifelse(is.na(Chicks_1) & Chicks_2 == 2, 2, Chicks_1),
         Chicks_1 = ifelse(is.na(Chicks_1) & Chicks_2 == 1, 1, Chicks_1),
         Notes = ifelse(!is.na(Notes), paste0(DateTime, ": ", Notes, ". "), ""), 
         Notes = paste0(Notes, collapse = "")) %>% 
  filter(nn == max(nn)) %>% 
  mutate(Chicks_2 = ifelse(Status2 == "Failed", 0, Chicks_2), 
         Status2 = ifelse(FullID %in% failed_nests$FullID & Status2 == "Uplifted", "Uplifted-failed", Status2)) %>% 
  dplyr::select(-c(DateTime, Eggs, Chicks, nn, Status)) %>% 
  rename("Status" = "Status2") %>% 
  distinct()

# If failed at egg stage, remove
failed_chick <- chicks %>% 
  filter(Status == "Failed" | Status == "Uplifted-failed") %>%
  filter(!FullID %in% failed_eggs$FullID) %>%
  mutate(across(Est_TranspondDate5:Est_FledgeDate, ~NA),
         Status = "Failed-chicks",
         Comments = str_squish(Comments))

# If chicks uplifted (but did not fail)
uplifted_chick <- chicks %>%
  filter(Status == "Uplifted")

# Only successful chicks
chicks <- chicks %>% 
  filter(Status != "Failed" , Status != "Uplifted-failed", Status != "Uplifted")

#failed_nests %>% filter(!FullID %in% c(failed_eggs$FullID, failed_chick$FullID))

# Checking chicks without egg record
xx <- chicks %>% filter(!FullID %in% eggs$FullID) %>% 
  unite("Comments", c(Comments, Notes), sep = " ")

```

### Eggs + Chicks + Totals
```{r ect}

combo_nests <- eggs %>% 
  full_join(chicks, by = c("FullID"), suffix = c("", "x")) %>% 
  group_by(FullID) %>% 
  mutate(HatchDate = HatchDatex, 
         Status = ifelse(is.na(Statusx), Status, Statusx)) %>%  
  unite("Comments", c(Comments, Commentsx, Notes, Notesx), sep = " ") %>% 
         #NLaid = pmax(Eggs_1, Eggs_2, na.rm = T), 
         #NHatched = pmax(Chicks_1, Chicks_2, na.rm = T)) %>% 
  dplyr::select(c(NestYear, `Nest ID`, Status, Est_LayDate, Est_HatchDate, HatchDate, UpliftDate, Est_FledgeDate, FledgeDate, NLaid, diffeggs, NHatched, diffchicks, Comments)) %>%
  filter(!is.na(NestYear)) %>%
  bind_rows(xx) %>%
  mutate(Comments = str_squish(str_remove(Comments, "NA")), 
        Chicks_2 = ifelse(Status != "Chicks", NA, NHatched)) %>% # THIS MAY NOT ALWAYS HOLD TRUE
  arrange(NestYear, `Nest ID`)

failed_all <- rbind(failed_eggs, failed_chick, uplifted_chick) %>%
  select(names(combo_nests))

combo_nests <- combo_nests %>%
  filter(!FullID %in% failed_all$FullID) %>%
  bind_rows(failed_all)

```

# TOTALS
# MAJOR ISSUES HERE! WRONG NUMBERS BECAUSE OF YEARS! PERHAPS NEED TO INDEX
```{r totals}
ccc <- unique(combo_nests$NestYear)

tots <- lapply(ccc, function(cc) {
  
  fn <- failed_all[failed_all$NestYear == cc,]
  cn <- combo_nests[combo_nests$NestYear == cc,]
  
  # Chicks per pair not being calculated correctly. 
  totals <- cn %>% 
    ungroup() %>%
    summarise(Total_nests = nrow(cn), 
              Nests_failed = nrow(fn),
              Nests_uplifted = nrow(cn[cn$Status == "Uplifted" | cn$Status == "Uplifted-failed",]),
              Nest_successrate = (Total_nests-Nests_failed)/Total_nests, 
              Eggs_laid = sum(NLaid, na.rm = T),
              Chicks_hatched = sum(NHatched, na.rm = T), 
              Chicks_fledged = sum(NHatched, na.rm = T), 
              Chicks_perpair = Chicks_fledged/Total_nests, 
              Chicks_peradult = Chicks_fledged/(Total_nests*2)) 
})

```

### Adding parent and chick marking data to dataframes
```{r parentid}

#############################################
##### START HERE. COMPARE PAIRS ACROSS YEARS
############################################
birdid_all <- birdid %>%
  filter(`Nest ID_marking` %in% chicks$`Nest ID`) %>% 
  dplyr::select(c(`Bird ID`, `Nest ID_marking`, `Age_marking`, DateTime_marking)) %>% 
  mutate(NestYear = ifelse(month(DateTime_marking) > 7, year(DateTime_marking), year(DateTime_marking)-1)) %>% 
  dplyr::select(-DateTime_marking) %>% 
  group_by(NestYear, `Nest ID_marking`, Age_marking) %>% 
  mutate(n = row_number()) %>% 
  unite(nn, Age_marking, n, sep = "") 

birdid_chicks <- birdid_all %>% 
  filter(#Year == yr, 
    nn %in% c("Chick1", "Chick2"))

cols <- rep(NA_real_, length(unique(birdid_all$nn)))
names(cols) <- rbind(sort(unique(birdid_all$nn)))

# number of visits
nvisits <- nests %>% 
  group_by(NestYear, `Nest ID`) %>% 
  summarise(nvisits = max(row_number()))

  parents <- nests %>%
    mutate(NestYear = ifelse(month(DateTime) > 7, year(DateTime), year(DateTime)-1)) %>%
    dplyr::select(NestYear, `Nest ID`, `Adult 1`, `Adult 2`) %>%
    group_by(NestYear, `Nest ID`) %>%
    pivot_longer(cols = 3:4, names_to = "Ind", values_to = "ID") %>%
    filter(!is.na(ID)) %>%
    mutate(Ind = "Adult") %>%
    distinct() %>%
    left_join(select(birdid, `Bird ID`, Sex), by = c("ID" = "Bird ID")) %>%
    mutate(Ind = ifelse(Sex == "Female" | Sex == "Unknown", "Adult1", "Adult2")) %>%
    arrange(NestYear, 'Nest ID')

parents_years <- parents %>%
  group_by(ID) %>%
  mutate(diffnest = ifelse(n_distinct(`Nest ID`) > 1, "diff", "same")) %>%
  ungroup() %>%
  group_by(`Nest ID`) %>%
mutate(diffpair = ifelse(n_distinct(ID) > 2, "diff", "same")) %>%
  arrange(`Nest ID`, NestYear) %>%
  pivot_wider(names_from = c(n_parent, NestYear), values_from = ID)

clipr::write_clip(parents_years)


  # Trying to identify which are new pairs. no idea how

nests_outcome <- birdid_all %>%
  pivot_wider(names_from = nn, values_from = `Bird ID`) %>% 
  tibble::add_column(!!!cols[!names(cols) %in% names(.)]) %>%
  right_join(combo_nests, by = c("NestYear", "Nest ID_marking" = "Nest ID")) %>% 
  rename("Nest ID" = "Nest ID_marking", "NFledged" = "Chicks_2") %>% 
  left_join(nvisits, by = c("NestYear", "Nest ID")) %>% 
  arrange(NestYear, `Nest ID`) %>% 
  ungroup() %>% 
  mutate_if(is.numeric, as.character) %>%
  mutate_if(is.Date, format, format = "%d/%m/%Y") %>% 
  mutate_all(as.character)  %>% 
  mutate(SeasonID = paste0(NestYear, `Nest ID`), .before = 1) %>% 
  mutate(EC1Fate = NA, EC2Fate = NA, EC1Intervention = NA, EC2Intervention = NA, .before = Comments) %>% 
  relocate(c(Chick1, Chick2, Est_LayDate:FledgeDate), .before = Comments) %>% 
  relocate(NHatched, .before = NFledged) %>% 
  dplyr::select(-Unknown1) %>% 
  rename('NestID' = `Nest ID`, "Adult1ID" = "Adult1", "Adult2ID" = "Adult2", 
         "Chick1ID" = "Chick1", "Chick2ID" = "Chick2", "Nvisits" = "nvisits") %>% 
  mutate(across(ends_with(c("1ID", "2ID")), str_replace_na, "UM"))

```

```{r}
openxlsx::write.xlsx(nests_outcome, paste0("./../ALL_DATA/Data/BreedingSeason_", yr, "_finalsummary.xlsx"), sheetName = paste("Breeding season", yr, sep = "_"), 
                     colNames = TRUE, rowNames = FALSE, append = FALSE)

#write.csv(nests_outcome, paste0("./../ALL_DATA/Data/BreedingSeason_", yr, "_finalsummary.csv"), row.names = FALSE)
```

### Getting information about the moult
```{r moult}
moult <- monitor %>%
  filter(`Nest activity` == "Moulting")

length(unique(moult$`Adult 1`))
length(unique(moult$`Nest ID`))

markedmoult <- moult %>% 
  filter(!is.na(`Adult 1`) | !is.na(`Adult 2`) | 
           !is.na(`Adult 3`) | !is.na(`Adult 4`)) %>% 
  select(`Nest ID`, `Adult 1`, `Adult 2`) %>% 
  pivot_longer(c(`Adult 1`, `Adult 2`), names_to = "n", values_to = "AdultID") %>% 
  filter(!is.na(AdultID)) %>% 
  select(-n) %>% 
  distinct()

notmoulted <- birdid %>% 
  select(`Nest ID_marking`, `Bird ID`, Age_marking) %>% 
  filter(!`Bird ID` %in% markedmoult$AdultID) %>% 
  filter(Age_marking != "Chick") 
```

### Getting information about resights
```{r resight}
cc <- c("Adult 1", "Adult 2", "Adult 3", "Adult 4", 
        "Chick 1 ID", "Chick 2 ID", "Chick 3 ID", "Chick 4 ID")

resight <- monitor %>%
  select(DateTime, `Nest ID`, all_of(cc) , Image.http) %>% 
  filter(DateTime >= start & DateTime <= end) %>%
  pivot_longer(all_of(cc), names_to = "n", values_to = "BirdID") %>% 
  group_by(BirdID) %>% 
  filter(!is.na(BirdID), DateTime == max(DateTime, na.rm = T)) %>%
  mutate(n = str_replace_all(n, " ID", ""))


chick_resights <- resight %>% 
  filter(DateTime >= non_br & DateTime <= end) %>% 
  filter(BirdID %in% birdid_chicks$`Bird ID`)
```  

```{r}
xxx <- monitor %>% 
  filter(DateTime>=tdt-7, 
         `Nest activity` != "Empty")

```

### Reading in cleaned yearly summary of breeding
```{r cleanedsum}
breeding <- read_excel("./../ALL_DATA/Data/BreedingSeason_2022_finalsummary_edited.xlsm")
```

################################################################################
### Weights
#### THERE ARE PROBLEMS HERE THAT NEED FIXING
```{r weights}
# temp <- nests %>% 
#   select(-starts_with("Chick 2")) %>% 
#   left_join(breeding[c(3, 6, 18:21)], by = c("Nest ID" = "NestID")) %>% 
#   mutate(across(c(HatchDate:FledgeDate), str_replace_all, "/", "-"), 
#          across(c(HatchDate:FledgeDate), as.Date, "%d-%m-%Y")) %>% 
#   mutate(`Chick 1 ID` = ifelse(is.na(`Chick 1 ID`), "c1", `Chick 1 ID`), 
#          days_hatch = difftime(DateTime, HatchDate, units = "days"), 
#          weeks_hatch = round(as.numeric(days_hatch)/7, 1)) %>% 
#   rename("ID" = `Chick 1 ID`, "Fate" = `Chick 1 status`, "Weight" = `Chick 1 weight`)
# 
# weights_chick <- nests %>% 
#   select(-starts_with("Chick 1")) %>% 
#   left_join(breeding[c(3, 6, 18:21)], by = c("Nest ID" = "NestID")) %>% 
#   mutate(across(c(HatchDate:FledgeDate), str_replace_all, "/", "-"), 
#          across(c(HatchDate:FledgeDate), as.Date, "%d-%m-%Y")) %>% 
#   mutate(`Chick 2 ID` = ifelse(is.na(`Chick 2 ID`), "c2", `Chick 2 ID`)) %>% 
#   rename("ID" = `Chick 2 ID`, "Fate" = `Chick 2 status`, "Weight" = `Chick 2 weight`) %>% 
#   bind_rows(temp) %>% 
#   arrange(`Nest ID`, ID) %>% 
#   filter(!is.na(Weight)) %>% 
#   mutate(days_hatch = as.numeric(days_hatch)) %>% 
#   unite(col = ID, `Nest ID`, ID, sep = "-", remove = FALSE, na.rm = TRUE) #%>% 
# #mutate(Underweight = ifelse(Weight <= 700 & days_hatch >= 42, "Concern", "Ok"), 
# #       Underweight = ifelse(Weight <= 600 & days_hatch >= 42, "Intervene", Underweight)) %>% 
# #select(-Status2)
# clipr::write_clip(weights_chick)
# 
# ggplot(data = weights_chick, aes(x = days_hatch, y = Weight, 
#                                  #shape = Status, 
#                                  color = `Nest ID`, 
#                                  group = ID))
# 
# ggplot(data = weights_chick, aes(x = DateTime, y = Weight, 
#                                  #shape = Status, 
#                                  color = `Nest ID`, 
#                                  group = ID)) +
#   geom_point() +
#   #geom_line() +
#   geom_rug() +
#   theme_minimal() +
#   guides(color = FALSE)

```

```{r ecfateplot}
# ecfate <- read_excel("nests_ecfate_18112022.xlsx")
# ecfate$code <- as.factor(ecfate$code)
# #ccord <- ecfate %>% filter(!is.na(Lat))
# #coordinates(ccord) <- ~Lat+Long
# 
# library(leaflet)
# pal <- colorFactor(c("yellow", "blue", "purple", "orange", "red"), ecfate$code)
# lab <- as.character(ecfate$code)
# 
# x <- leaflet() %>% 
#   #addCircles(lng = ~Long, lat = ~Lat) %>% 
#   addTiles('http://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}',
#            options = providerTileOptions(noWrap = TRUE), group = "World Imagery") %>%
#   # addTiles('http://server.arcgisonline.com/ArcGIS/rest/services/Reference/World_Boundaries_and_Places/Mapserver/tile/{z}/{y}/{x}',
#   #          options = providerTileOptions(noWrap = TRUE),group = "Labels") %>% 
#   addCircleMarkers(data = ecfate, lat = ~Lat, lng = ~Long,
#                    radius = 3,
#                    color = ~pal(ecfate$code),
#                    stroke = FALSE, fillOpacity = 1) %>%
#   leaflet::addLegend(pal = pal, values = lab, opacity = 1, position = "bottomleft") %>%
#   fitBounds(173.00275,-43.871,173.015,-43.866)
# 
# library(mapview)
# library(htmlwidgets)
# mapshot(x, file = "~/map_activefailednests.png")
# saveWidget(x, selfcontained = T, file = "~/map_activefailednests.html")
# 
# resfactor <- 3
# png(filename=x, res = 72*resfactor, height=640*resfactor, width=640*resfactor)
```

```{r}
# ggplot(data = allstats2[allstats2$name != "nest_monitored",]) +
#   geom_line(aes(x = week, y = count, group = name, colour = name), size = 1) +
#   scale_colour_manual(values = c("darkgreen", "orange", "deepskyblue", "red", "purple", "magenta")) +
#   geom_point(aes(x = week, y = count, group = name, fill = name)) +
#   scale_fill_manual(values = c("darkgreen", "orange", "deepskyblue", "red", "purple", "magenta")) +
#   theme_minimal() +
#   theme(axis.title = element_blank(), 
#         legend.title = element_blank(), 
#         axis.text.y = element_text(size = 14), 
#         axis.text.x = element_text(angle = 45, size = 11, hjust = .9),
#         legend.text = element_text(size = 14), 
#         legend.position = "top")

```

